E1: ENRON Sentiment

### 2016-03-25 paper/paper.tex
added ACKs

\section{Experiments}
\label{sec:exp}
TODO

@@

\section{Acknowledgments}
SURFsara maybe?...

\clearpage
\balance
\bibliographystyle{abbrv}
\bibliography{bibliography}

\begin{appendix}
TODO

\section{BLA BLA}
TODO

\end{appendix}

>>>>

\section{Experiments}
\label{sec:exp}
In this section we briefly explain the experiments run in order to obtain our results.

@@

\section{Acknowledgments}
We would like to remark our thankfulness to our teachers Peter Boncz and Hannes M{\"u}hleisen for their inspiration and support during this work and the LSDE 15-16 course held at Vrije Universiteit Amsterdam.
Last but not least we want to thank SURFsara\footnote{\url{www.surf.nl}} for the.

%\clearpage
%\balance
\bibliographystyle{abbrv}
\bibliography{bibliography}

%\begin{appendix}
%TODO
%\section{BLA BLA}
%TODO
%\end{appendix}
